Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two tunables of Hardness
Manipulation.

@@

\subsection{State-of-The-Art Defenses}

@@

	 What if we mix HM(RM) and HM(SM)?
		works but not good enough.

	 Note, naive combination of benign training and adv train does not lead to better result, why? mix 0.5

\subsection{Graduate Adversary}

>>>>

The $H_\mathsf{S}$ and $H_\mathsf{D}$ are the only two adjustable items of
Hardness Manipulation.

@@

\subsection{State-of-The-Art Defenses}
\label{sec:b1}

@@

According to the experimental results, HM[$\mathcal{R},\mathcal{M}$] achieves 
a high ERS and adversarial training efficiency, but suffers from a low R@1.
%
HM[$\mathcal{S},\mathcal{M}$] achieves a high R@1, but its ERS and efficiency
could be further improved.
%
They can be mixed for adversarial training with a probability $p$ to combine
their advantages, but the eventual overall performance is still lower than
that of HM[$\mathcal{S},g_\mathsf{LGA}$] according to our observation.

\subsection{Graduate Adversary}
\label{sec:b3}
